% Document Definition
\documentclass[10pt, letterpaper]{resume}

\usepackage[default]{opensans}
\usepackage[T1]{fontenc}
\setmainfont{OpenSans}[
  Extension = .ttf,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic,
]

\name{EMERSON FORD}
\email{emersontford@gmail.com}
\github{emersonford}
\linkedin{emerson-ford}

\begin{document}
\maketitle

{\centering
 Fifth-year CS student at the University of Utah interested in infrastructure and low-level systems.
 \par
}

\section{EDUCATION}
 {\centering
  \textbf{University of Utah}

  Double BS in Honors Computer Science \& Mathematics, Statistics Emphasis

  May 2016 -- May 2021 | GPA: 3.77 / 4.0

  \par
 }
\vspace{10pt}
{{\fontseries{sb}\selectfont Thesis Topic:} RDMA Networking in HPC Containers}
\smallbreak%
{{\fontseries{sb}\selectfont Relevant Course Work:}
Advanced Operating Systems, Programming Languages, Computer Networks, Parallel Computing, Intro to Data Science, Applied Statistics, Cryptography, Distributed Systems*, Graduate Algorithms* {\footnotesize(*currently enrolled)}}
\smallbreak%
{{\fontseries{sb}\selectfont Skills:} Python 3, Go, C++, C, MySQL, \LaTeX, Ruby, Rust, Java, Bash, Linux, Git, Mercurial, Docker, Kubernetes, Ansible, Puppet, AWS, Node.js, Thrift, RPC, Terraform, asynchronous programming, networking}

\section{EXPERIENCE}
\subsection{University of Utah -- Center for High Performance Computing}
Student Intern | Salt Lake City | May 2017 -- Present
\begin{itemize}
    \item Developed a \href{https://github.com/slateci/slate-puppet}{Puppet module} to fully instantiate Kubernetes clusters for the \href{https://slateci.io}{SLATE research project}.
    \item Deployed and manage a Foreman/Puppet/Ansible stack to automate host provisioning and management.
 \item Prototyped OpenStack, Emulab, and OpenNebula for the development of a HPCaaS environment.
\end{itemize}

\subsection{Facebook}
Production Engineer Intern | Seattle | Summer 2018 \& Summer 2019 \& Summer 2020
\begin{itemize}
    \item Worked with the Messenger Infra team to add flow control functionality to a C++ RPC proxy for \href{https://engineering.fb.com/production-engineering/building-mobile-first-infrastructure-for-messenger/}{Iris}.
 \item Developed two services from scratch in Python 3 to automate stress testing of storage nodes for the Storage Platform team and to manage the lifecycles for all hosts powering \href{https://research.fb.com/wp-content/uploads/2016/11/scuba-diving-into-data-at-facebook.pdf}{Scuba} for the Monitoring team.
 \item Assisted and mentored other interns in learning Facebook's tools and infrastructure.
\end{itemize}

\section{LEADERSHIP}
\subsection{HackTheU}
Chief Director | May 2017 -- December 2019 / Advisory Director | December 2019 -- Present

\begin{itemize}
  \item Managed a team of 20 to host Utah's largest hackathon with over 300 attendees in 2019.
  \item Automated hackathon infrastructure deployment on AWS with Terraform, Ansible, and Github Actions.
\end{itemize}

\subsection{School of Computing Undergraduate Advisory Committee}
Member | May 2017 -- October 2020 / Chair | October 2020 -- Present
\begin{itemize}
  \item Host events for students and act as the student-department liaison for the School of Computing.
\end{itemize}

\section{PROJECTS / ACTIVITIES}
\begin{itemize}
 \item Reproduced remote cache hit/miss timing differences over RDMA as detailed in the \href{https://download.vusec.net/papers/netcat_sp20.pdf}{NetCAT} paper.
 \item Developed a Lisp-like language with parsing, types, and classes in Racket for Programming Languages.
 \item Implemented MapReduce and Raft in Go for Distributed Systems.
 \item Second place winner of the \href{https://github.com/lucidsoftware/ctf2019}{2019 Lucid Software Capture the Flag} competition.
\end{itemize}


\end{document}
